---
title: "Programming Assignment 3"
author: "Ziling Zhu"
date: "Last update: `r Sys.Date()`"
output:
  html_document:
    theme: yeti
---

# Load the dataset
```{r, echo = TRUE}
#set up tidyverse
library(tidyverse)
#load the dataset languageR
library(languageR)
```

## Tidy the dataset
```{r, echo = TRUE}
#show that the dataset is tidy
str(english)
#give the first six examples of the tidy dataset
head(english)
```

## Calculate descriptive statistics
```{r, echo = TRUE}
#descriptive statistics of each variable
summary(english)
```

## Build a bivariate regression model
```{r, echo = TRUE}
#build a bivariate regression model
model <- lm(Familiarity ~ WrittenFrequency, data = english)
#show the model details
summary(model)
```

## Plot
```{r, echo = TRUE}
#import the dataset english
english %>% 
#pipe it into ggplot2
ggplot(aes(x = WrittenFrequency, y = Familiarity)) + 
#draw a scatterplot
  geom_point(alpha = 0.05) +
#draw the regression line
  geom_smooth(method = "lm", color = "navy", size = 1, se = FALSE) +
#put a label for the regression line
  annotate(geom = "text", x = 10, y = 5.5,
           label = "y = 0.49x + 1.32",
           family = "Palatino") +
#put labels for the x-axis, y-axis, and title
  labs(x = "WrittenFrequency", y = "Familiarity",
       title = "Positive Correlation of Written Frequency and Familiarity") +
#set a beautiful theme
  theme_minimal() +
#set a beautiful font
  theme_test(base_family = "Palatino")
```

## General observations
The two continuous variables that I have selected are **WrittenFrequency** and **Familiarity**. The p-value is lower than 0.05, so the positive correlation of the two variables is statistically significant. That means **Familiarity** is positively correlated with **WrittenFrequency**.

In the dataset, we can preliminarily conclude that the more frequently an English word is written, the more familiar English users rate it to be.
